---
title: "Report"
author: "Lam Phung Khanh"
date: "7/30/2020 (update: `r Sys.Date()`)"
output:
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Objectives

## Methods

### Contact network

* BBC Pandemic data
* Google Mobility data
* Facebook data
* Contact tracing data

### Epidemic model

* a branching process model
* the number of potential secondary cases produced by each individual is drawn from a negative binomial distribution with a mean equal to the reproduction number, and heterogeneity in the number of new infections produced by each individual
*  Each potential new infection was assigned a time of infection drawn from the serial interval distribution. 
*  Secondary cases were only created if the person with the infection had not been isolated by the time of infection
*  in the model, a reduced delay from onset to isolation would reduce the average number of secondary cases

* We initialised the branching process with five, 20, or 40 cases to represent a newly detected outbreak of varying size. 
* Initial symptomatic cases were then isolated after symptom onset with a delay drawn from the onset-toisolation distribution (table). 
* Isolation was assumed to be 100% effective at preventing further transmission; therefore, in the model, failure to control the outbreak resulted from the incomplete contact tracing and the delays in isolating cases rather than the inability of isolation to prevent further transmission. 
* Either 100% or 90% of cases became symptomatic, and all symptomatic cases were eventually reported.

* Each newly infected case was identified through contact tracing with probability ρ. 
* Secondary cases that had been traced were isolated immediately on becoming symptomatic. 
* Cases that were missed by contact tracing (probability 1–ρ) were isolated when they became symptomatic, with a delay drawn from the onset-to -isolation distribution

* In addition, each case had an independent probability of being subclinical, and was therefore not detected either by self-report or contact tracing. 
* New secondary cases caused by a subclinical case were missed by contact tracing and could only be isolated on the basis of symptoms. 
* The model included isolation of symptomatic individuals only—ie, no quarantine, so isolation could not prevent transmission before symptom onset. 
* In the model, subclinical cases were never isolated, whereas symptomatic cases might transmit before symptoms appear, but were eventually isolated. 
* Quarantining contacts of cases (ie, individuals who are not yet symptomatic, and might not be infected) requires a considerable investment in public health resources, and has not been widely implemented for all contacts of cases
* However, some countries have adopted a quarantine or self-quarantine policy for airline travellers who have returned from countries with confirmed COVID-19 transmission.

### Lockdown strategies

* Nothing
* Contact-tracing only
* Full lockdown
* Responsive lockdown

### Cost-effectiveness assessment

#### Outcomes

* Number of cases
* Number of quarantine
* Number of test

* Cost

## Results
### Contact network
```{r}
# simulate population
pop <- pop_sim(n = 500, hh_max = 8, hh_mean = 4, ws_max = 100, ws_mean = 50, seed = 1)
```

Check structure of population

* Household

```{r}
hh <- pop %>%
  group_by(hh_id) %>%
  summarise(n = n(), .groups = "drop")
ggplot(data = hh) + geom_histogram(aes(x = n), binwidth = 1)
```

* Work/school

```{r}
ws <- pop %>%
  group_by(ws_id) %>%
  summarise(n = n(), .groups = "drop")
ggplot(data = ws) + geom_histogram(aes(x = n), binwidth = 1)
ggplot(data = filter(ws, n > 1)) + geom_histogram(aes(x = n), binwidth = 1)
```
```{r}
## simulate contact
contactnet <- contact_sim(pop = pop,
                          assume = cbind(hh = c(0.1, 0.2, 0.4, 0.3),
                                         ws = c(0.69, 0.2, 0.1, 0.01),
                                         ot = c(0.889, 0.1, 0.01, 0.001)),
                          seed = 1)
```

Describe contact network

```{r}
sum_contactnet <- contactnet %>%
  group_by(case_1) %>%
  summarise(n_0 = sum(value == 0),
            n_1 = sum(value == 1),
            n_2 = sum(value == 2),
            n_3 = sum(value == 3),
            n_4 = sum(value %in% c(1:3)),
            .groups = "drop") %>%
  gather(key = "type", value = "n", -case_1) %>%
  mutate(p = n/length(unique(contactnet$case_1)))
```

```{r}
ggplot(data = sum_contactnet, aes(x = type, y = p)) + geom_boxplot()
ggplot(data = sum_contactnet, aes(x = type, y = n)) + geom_boxplot() +
  scale_y_continuous(breaks = c(0, 10, 20, 30, 40, 50, 100, 200, 300, 400, 500))
```

Update contact daily

```{r}
contact_d1 <- contact_step(contact_setup = contactnet, day = 1, p = 0.99)
```


### Transmission rate and probability of infection

```{r}
p <- seq(from = 0, to = 1, by = 0.001)
rate <- -log(1 - p)

plot(x = p, y = rate)
```
### Scenarios
```{r}
pop <- pop_sim(n = 500, hh_max = 8, hh_mean = 4, ws_max = 100, ws_mean = 50, seed = 1)

## simulate contact
contactnet <- contact_sim(pop = pop,
                          assume = cbind(hh = c(0.1, 0.2, 0.4, 0.3),
                                         ws = c(0.69, 0.2, 0.1, 0.01),
                                         ot = c(0.889, 0.1, 0.01, 0.001)),
                          seed = 1)
```


#### No control

```{r}

```


## Discussions
